---
title: "COMPSCIX 415.2 Homework 5/Midterm"
Autor: "Diana Cuesta"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## The tidyverse packages (3 points)
By now you’ve used at least five different packages from the tidyverse for plotting, data munging, reshaping data, importing/exporting data, and using tibbles (the tibble package is used for this without you even realizing it’s there).

###Can you name which package is associated with each task below?
Plotting - ggplot2
Data munging/wrangling - dplyr
Reshaping (speading and gathering) data - tidyr
Importing/exporting data - readr 

###Now can you name two functions that you’ve used from each package that you listed above for these tasks?

Plotting - ggplot() and geom_point()
Data munging/wrangling - spread(), gather() 
Reshaping data - summarize(), groupby()
Importing/exporting data - read_cvs() and write_cvs()

##R Basics (1.5 points)

1)Fix this code with the fewest number of changes possible so it works:
My_data.name___is.too00ooLong! <- c( 1 , 2   , 3 )
```{r}
My_data_name___is_too00ooLong <- c( 1 , 2   , 3 )
My_data_name___is_too00ooLong
```

2)Fix this code so it works:
my_string <- C('has', 'an', 'error', 'in', 'it)
```{r}
my_string <- c('has','an','error','in','it')
my_string
```

3)Look at the code below and comment on what happened to the values in the vector.
my_vector <- c(1, 2, '3', '4', 5)
my_vector

```{r}
my_vector <- c(1, 2, '3', '4', 5)
my_vector
```

THe values in the vector were converted to strings.

##Data import/export (3 points)
Download the rail_trail.txt file from Canvas (in the Midterm Exam section) and successfully import it into R. Prove that it was imported successfully by including your import code and taking a glimpse of the result.

Export the file into a comma-separated file and name it “rail_trail.csv”. Make sure you define the path correctly so that you know where it gets saved. Then reload the file. Include your export and import code and take another glimpse.
 
```{r}
library(tidyverse)
heights <- read_csv("/Users/dianacuesta/Compscisx-415-2/rail_trail.csv")
glimpse(heights)
```

###Visualization (6 points)
Critique this graphic: give only three examples of what is wrong with this graphic. Be concise.
1) Graph is really difficult to read. Cateogries don't up to 100%. Colors doesn't say much. We don't know what the colors or numbers are representing. The categories are overlapping, there are women and man that are on all ages representing in other categories. Not sure a pie is the correct graph to represent the data to be anaylized.

```{r}
library(ggplot2)
data(diamonds)
ggplot(diamonds, aes(cut, carat,fill=color)) + geom_boxplot() + ggtitle("Diamond Price according Cut") + xlab("Type of Cut") + ylab("Carat") + coord_flip()

```

Improved Graph
```{r}
ggplot(diamonds, aes(factor(cut), carat, fill=cut)) + geom_boxplot() + ggtitle("Diamond Carat") + xlab("Type of Cut") + ylab("Carat") + coord_flip()
```

###Data munging and wrangling (6 points)
Is this data “tidy”? If yes, leave it alone and go to the next problem. If no, make it tidy. Note: this data set is called table2 and is available in the tidyverse package. It should be ready for you to use after you’ve loaded the tidyverse package.

Answer: It is not tydy.
 
```{r}
library(tidyverse)

table2 %>%
    spread(key = type, value = count)
```


