---
title: "COMPSCIX 415.2 Homework 3"
output: html_document
Autor: Diana Cuesta
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
###Section 3.8.
###3.8.1 Exercise 1.
What is the problem with this plot? How could you improve it?
```{r}
library(ggplot2)
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) +
  geom_point()
```
The problem is that there are multiple observations for x and Y. I would fix it by adding the position adjusdment value.
```{r}
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) +
  geom_point(position = "jitter")
```
###3.8.1 Exercise 2
###What parameters to geom_jitter() control the amount of jittering?
there are two parameters: width and height. They control the amount of vertical and horizontal jitter.

###3.8.1 Exercise 3
####Compare and contrast geom_jitter() with geom_count()
```{r}
ggplot(mpg, aes(cty, hwy)) +
 geom_count()
```
geom_count counts the number of observations at each location, then maps the count to point area
It useful when you have discrete data and overplotting.
```{r}
ggplot(mpg, aes(cty, hwy)) +
 geom_jitter()
```
###3.8.1 Exercise 4
####What’s the default position adjustment for geom_boxplot()? Create a visualisation of the mpg dataset that demonstrates it.

The default position for geom_boxplot is position_dodge
```{r}
ggplot(data = mpg, mapping = aes(x = drv, y = hwy, colour=class)) +
 geom_boxplot()
```

```{r}
ggplot(data = mpg, aes(x = drv, y = hwy, colour=class)) +
  geom_boxplot(position = "identity")
```

##Section 3.9.1
###3.9.1 Exercise 2
#### What does labs() do? Read the documentation.
The labs function adds labels for different scales and the title of the plot.

####What does the plot below tell you about the relationship between city and highway mpg? Why is coord_fixed() important? What does geom_abline() do?
```{r}
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) +
  geom_point() +
  geom_abline() +
  coord_fixed()
```
Coord_fixed makes the angle be at a 45 degree. This makes it easy to compare the highway and city 

##Section 4.4: 
###4.4. Exercise 1
###Why does this code not work?
```{r}
my_variable <- 10
my_varıable
```

Because they are not the same variables: one is using the "i" and the second one is using "|". R is case sensitive.
##Section 4.4: 
###4.4. Exercise 2
####Tweak each of the following R commands so that they run correctly:
```{r}
library(tidyverse)

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy))

fliter(mpg, cyl = 8)
filter(diamond, carat > 3)
```
There is an error : Function fliter does not exist. because there is an mis-spell it should be filter

```{r}
library(tidyverse)

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy))

filter(mpg, cyl = 8)
filter(diamond, carat > 3)
```
There is also a problem on this line filter(mpg, cyl = 8). One single "=" is used for assignation. Here is this statement we should use "==" to compare.
```{r}
library(tidyverse)

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy))

filter(mpg, cyl == 8)
filter(diamond, carat > 3)
```
##Section 5.2: 
###Exercise 1
####Find all flights that

Had an arrival delay of two or more hours
Flew to Houston (IAH or HOU)
Were operated by United, American, or Delta
Departed in summer (July, August, and September)
Arrived more than two hours late, but didn’t leave late
Were delayed by at least an hour, but made up over 30 minutes in flight
Departed between midnight and 6am (inclusive)

```{r}
library("nycflights13")
library("tidyverse")
glimpse(flights)
```

