---
title: "COMPSCIX 415.2 Homework 5/Midterm"
Autor: "Diana Cuesta"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## The tidyverse packages (3 points)
By now you’ve used at least five different packages from the tidyverse for plotting, data munging, reshaping data, importing/exporting data, and using tibbles (the tibble package is used for this without you even realizing it’s there).

###Can you name which package is associated with each task below?
Plotting - ggplot2
Data munging/wrangling - dplyr
Reshaping (speading and gathering) data - tidyr
Importing/exporting data - readr 

###Now can you name two functions that you’ve used from each package that you listed above for these tasks?

Plotting - ggplot() and geom_point()
Data munging/wrangling - spread(), gather() 
Reshaping data - summarize(), groupby()
Importing/exporting data - read_cvs() and write_cvs()

##R Basics (1.5 points)

1)Fix this code with the fewest number of changes possible so it works:
My_data.name___is.too00ooLong! <- c( 1 , 2   , 3 )
```{r}
My_data_name___is_too00ooLong <- c( 1 , 2   , 3 )
My_data_name___is_too00ooLong
```

2)Fix this code so it works:
my_string <- C('has', 'an', 'error', 'in', 'it)
```{r}
my_string <- c('has','an','error','in','it')
my_string
```

3)Look at the code below and comment on what happened to the values in the vector.
my_vector <- c(1, 2, '3', '4', 5)
my_vector

```{r}
my_vector <- c(1, 2, '3', '4', 5)
my_vector
```

THe values in the vector were converted to strings.

##Data import/export (3 points)
Download the rail_trail.txt file from Canvas (in the Midterm Exam section) and successfully import it into R. Prove that it was imported successfully by including your import code and taking a glimpse of the result.

Export the file into a comma-separated file and name it “rail_trail.csv”. Make sure you define the path correctly so that you know where it gets saved. Then reload the file. Include your export and import code and take another glimpse.
 
```{r}
library(tidyverse)
heights <- read_csv("/Users/dianacuesta/Compscisx-415-2/rail_trail.csv")
glimpse(heights)
```


