---
title: "COMPSCIX 415.2 Homework 4 - Cuesta"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
## R Markdown
##5.6.7 Exercises
### Exercise 2
####Come up with another approach that will give you the same output as not_cancelled %>% count(dest) and not_cancelled %>% count(tailnum, wt = distance) (without using count()).
```{r}
library(nycflights13)
library(tidyverse)
flights

```
```{r}
flights %>%
  group_by(dest) %>%
  summarise(n = length(dest))
```

####Look at the number of cancelled flights per day. Is there a pattern? Is the proportion of cancelled flights related to the average delay?
```{r}
results <-
  flights %>%
  mutate(canceled_flights = (is.na(arr_delay) | is.na(dep_delay))) %>%
  group_by(year, month, day) %>%
  summarise(prop_canceled = mean(canceled_flights),
            avg_delay = mean(dep_delay, na.rm = TRUE))

results


 ggplot(results, aes(x = avg_delay, prop_canceled)) +
  geom_point() +
  geom_smooth()
```

Yes, there are a correlation between the number of flights cancelled per day and the average delay.

####What does the sort argument to count() do. When might you use it?
The sort argument to count sorts the results in order. It can be used this anytime we count and the sort.


