---
title: "Homework_2_Cuesta"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

###Excersises 3.4.2

```{r}
library(ggplot2)
ggplot(data = mpg)

```

###How many rows are in mpg? How many columns?
234 rows, 11 columns

###What does the drv variable describe? Read the help for ?mpg to find out.
f = front-wheel drive, r = rear wheel drive, 4 = 4wd

###Make a scatterplot of hwy vs cyl.
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = hwy, y = cyl, color = class))
```

###What happens if you make a scatterplot of class vs drv? Why is the plot not useful?
```{r}
library(ggplot2)
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = class, y = cyl, shape = class))
```

###What’s gone wrong with this code? Why are the points not blue?
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, color = "blue"))
```
The problem is that the color blue is assigned to Color instead of the class. Correct code should be like 
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, color = class))
```

